---
title: "Case Study in Class"
author: "Jake Vettoretti"
date: "2025-10-07"
output: html_document
---

## Case Study 

Loading data
```{r}
library(tidyverse)
library(dplyr)
library(p8105.datasets)
library(leaflet)
data(nyc_airbnb)
```


#Brainstorming questions
*Pick neighborhood, investigate price
  *Do dates affect price?
*Does type of unit affect rating/price?
  *What about zip codes?
*Which rental as the highest reviews?
*Are there any connections between price and other var?
*How else did the pandemic affect AirBNB in NYC?
*Does the name of the rental affect the price/rating?
*Does name of rental affect price/rating?

Looking at prices
```{r}
nyc_airbnb |> 
  drop_na(price) |> 
  group_by(neighbourhood_group) |> 
  summarize(
    mean_price = mean(price),
    min_price = min(price),
    max_price = max(price),
  )
```

What about room tupe in a given neighborhood
```{r}
nyc_airbnb |> 
  drop_na(price) |> 
  group_by(room_type, neighbourhood_group) |> 
  summarize(
    mean_price = mean(price)
  ) |> 
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )
```

```{r}
nyc_airbnb |> 
  group_by(room_type, neighbourhood_group) |> 
  count(room_type)
```


Making plots
```{r}
nyc_airbnb |> 
  ggplot(aes(x=price)) +
  geom_histogram() +
  facet_grid(room_type ~ neighbourhood_group) 
  scale_x_continuous(limits = c(0, 1000))
```

Manhattan prices
```{r}
nyc_airbnb |> 
  filter(neighbourhood_group == "Manhattan",
         price < 500,
         room_type == "Entire home/apt") |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  ggplot(aes(x=neighbourhood, y=price))+
  geom_violin() +
  theme(axis.text.x = element_text(angle=90, hjust =1, vjust = 0.5))
```

Remember to look at extreme values
```{r}
nyc_airbnb |> 
  filter(price>9000)
```

```{r}
nyc_airbnb |> 
  filter(calculated_host_listings_count > 30)
```

Keep looking at location
```{r}
nyc_airbnb |> 
  filter(neighbourhood_group == "Manhattan",
         price < 1000,
         room_type == "Entire home/apt") |> 
  ggplot(aes(x=lat, y=long, color=review_scores_location))+
  geom_point()
```

Can we make a better map?
```{r}

pal <-colorNumeric(
  palette = "Viridis",
  domain = nyc_airbnb$review_scores_location
)
nyc_airbnb |> 
  filter(neighbourhood_group == "Manhattan",
         price < 1000,
         room_type == "Entire home/apt") |> 
  sample_n(25) |> 
  leaflet() |> 
  addProviderTiles(providers$CartoDB.Positron) |> 
  addCircleMarkers(
    ~long, ~lat,
    color = ~pal(review_scores_location),
    radius = 2)
```






