---
title: "Case Study in Class"
author: "Jake Vettoretti"
date: "2025-10-07"
output: html_document
---

## Case Study 

Loading data
```{r}
library(tidyverse)
library(dplyr)
library(p8105.datasets)
data(nyc_airbnb)
```


#Brainstorming questions
*Pick neighborhood, investigate price
  *Do dates affect price?
*Does type of unit affect rating/price?
  *What about zip codes?
*Which rental as the highest reviews?
*Are there any connections between price and other var?
*How else did the pandemic affect AirBNB in NYC?
*Does the name of the rental affect the price/rating?
*Does name of rental affect price/rating?

Looking at prices
```{r}
nyc_airbnb |> 
  drop_na(price) |> 
  group_by(neighbourhood_group) |> 
  summarize(
    mean_price = mean(price),
    min_price = min(price),
    max_price = max(price),
  )
```
What about room tupe in a given niehgborhhod
```{r}
nyc_airbnb |> 
  drop_na(price) |> 
  group_by(room_type, neighbourhood_group) |> 
  summarize(
    mean_price = mean(price)
  ) |> 
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )
```




Understanding the variables inside
```{r, echo =FALSE}
#str(nyc_airbnb)

#nyc_airbnb |> 
#  count(room_type)

#nyc_airbnb |> 
#  count(neighbourhood_group)
```


